Build Operating Models for SA Species

### 2022-06-02 BuildOM/BuildOMAssess2OM.Rmd
move large files out of repo

```{r user}
length_sc <- 0.1 # Scalar (multiplier) to convert length units. MSEtool examples seem to use cm whereas BAM uses mm.
generate_Hist <- TRUE # Switch for running Simulate on all of the OM to generate Hist objects. (takes a while)
plot_Hist <- TRUE # Plot hist objects

@@

@@

  Data_name_i <- gsub("rdat","Data",rdat_name_i)
  Data_i <- rdat2Data(rdat_i, Mat_age1_max=Mat_age1_max, length_sc = length_sc,nsim=nsim)

@@

```{r build OM Assess2OM, eval=TRUE}
list_Nage_F0_pr_sc <- list() # List for storing values of Nage_F0_pr_sc (for plotting hist compared to BAM)
vec2mat <- function(vec){
  matrix(vec,nrow=dim(naa)[2],ncol=dim(naa)[3],byrow=FALSE,
                    dimnames=dimnames(naa)[2:3])
}

@@

 # Save rdat modifications
 rdatmods_name_i <- gsub("rdat","rdatmods",rdat_name_i)
 assign(rdatmods_name_i,
        list(
          "Name"=Name_i,
          "CurrentYr" = CurrentYr_i,
          "steep"=steep_i,
          "R0"=R0_i,
          "a.series"=a.series_i,
          "Nage_F0_pr_sc" = Nage_F0_pr_sc,
          "N.age" = t(naa_mat2[,-1]),
          "F.age" = t(faa_mat2[,-1]),
          "B.age" = t(naa_mat2[,-1])*t(mat_waa_klb)

          )
        )

@@

 if(AddInd_endyr_only){
   # Identify which indices are available (not NA) in the terminal year of the assessment
   AddInd_endyr_ix <- which(!is.na(AddInd[1,,dim(AddInd)[3]])) # Just uses the first sim!!
   AddInd <- AddInd[,AddInd_endyr_ix,,drop=FALSE]
   CV_AddInd <- CV_AddInd[,AddInd_endyr_ix,,drop=FALSE]
   AddIndV <- AddIndV[,AddInd_endyr_ix,,drop=FALSE]
   AddIndType <- AddIndType[AddInd_endyr_ix]
   AddIunits <- AddIunits[AddInd_endyr_ix]
 }

@@

 assign(OM_name_i,OM_i)
}  
```

@@

```{r generate Hist}
if(generate_Hist){

@@

```{r plot Hist with bam  results, eval=TRUE}
if(plot_Hist){
 pdf("HistBam.pdf")
CIpct = 95

@@

>>>>

```{r user}
length_sc <- 0.1 # Scalar (multiplier) to convert length units. MSEtool examples seem to use cm whereas BAM uses mm.
generate_Hist <- TRUE # Switch for running Simulate on all of the OM to generate Hist objects. (takes a while)
plot_Hist <- TRUE # Plot hist objects
plot_pdf <- TRUE

@@

```{r functions}
# color function like rainbow() but without yellow (or indigo)
blues <- colorRampPalette(c("darkblue","lightblue"))
grays <- colorRampPalette(c("black","lightgray"))
```

@@

  Data_name_i <- gsub("rdat","Data",rdat_name_i)
  Data_i <- rdat2Data(rdat_i, Mat_age1_max=Mat_age1_max, length_sc = length_sc,nsim=nsim, AddInd_order = "CVlo")

@@

```{r build OM Assess2OM, eval=TRUE}
rdatmods <- list() # List for saving rdat modifications used when plotting bam results compared with Hist objects
list_Nage_F0_pr_sc <- list() # List for storing values of Nage_F0_pr_sc (for plotting hist compared to BAM)
vec2mat <- function(vec){
  matrix(vec,nrow=dim(naa)[2],ncol=dim(naa)[3],byrow=FALSE,
                    dimnames=dimnames(naa)[2:3])
}

@@

 # Save rdat modifications
 rdatmods_name_i <- gsub("rdat","rdatmods",rdat_name_i)
 rdatmods_i <- list(
          "Name"=Name_i,
          "CurrentYr" = CurrentYr_i,
          "steep"=steep_i,
          "R0"=R0_i,
          "a.series"=a.series_i,
          "Nage_F0_pr_sc" = Nage_F0_pr_sc,
          "N.age" = t(naa_mat2[,-1]),
          "F.age" = t(faa_mat2[,-1]),
          "B.age" = t(naa_mat2[,-1])*t(mat_waa_klb)
          )
 assign(rdatmods_name_i,rdatmods_i)
 rdatmods[[Name_i]] <- rdatmods_i

@@

 # # Determine the order of indices from most precise to least precise, and sort the corresponding slots
 # # This will ensure the the most precise index is in the first column, and will therefore be used 
 # # for interim analysis based on an index.
 # o_CV_AddInd <- order(apply(CV_AddInd,2,function(x){mean(x,na.rm=TRUE)}))
 # 
 # AddInd <- AddInd[,o_CV_AddInd,,drop=FALSE]
 # CV_AddInd <- CV_AddInd[,o_CV_AddInd,,drop=FALSE]
 # AddIndV <- AddIndV[,o_CV_AddInd,,drop=FALSE]
 # AddIndType <- AddIndType[o_CV_AddInd]
 # AddIunits <- AddIunits[o_CV_AddInd]

 if(AddInd_endyr_only){
   # Identify which indices are available (not NA) in the terminal year of the assessment
   AddInd_endyr_NA <- is.na(AddInd[1,,dim(AddInd)[3]])
   if(any(!AddInd_endyr_NA)){
     AddInd_endyr_ix <- which(!AddInd_endyr_NA) # Just uses the first sim, but that should be fine
   }else{
     message(paste(Name_i,": No indices available in the terminal year of the assessment. Using the latest index available for AddInd."))
     AddInd_LastYearAvail <- apply(AddInd[1,,,drop=FALSE],2,function(x){max(which(!is.na(x)))})
     AddInd_endyr_ix <- AddInd_LastYearAvail==max(AddInd_LastYearAvail)
   }
   AddInd <- AddInd[,AddInd_endyr_ix,,drop=FALSE]
   CV_AddInd <- CV_AddInd[,AddInd_endyr_ix,,drop=FALSE]
   AddIndV <- AddIndV[,AddInd_endyr_ix,,drop=FALSE]
   AddIndType <- AddIndType[AddInd_endyr_ix]
   AddIunits <- AddIunits[AddInd_endyr_ix]
 }

@@

 assign(OM_name_i,OM_i)
}
save(rdatmods,file="rdatmods.RData")
```

@@

```{r generate Hist, eval=TRUE}
if(generate_Hist){

@@

```{r plot Hist with bam  results, eval=FALSE}
if(plot_Hist){
 pdf("HistBam.pdf")
CIpct = 95

@@

```{r plot Hist with bam  results, eval=TRUE}
if(plot_Hist){
CIpct  <-  95

#commonNames <- gsub(".*_(.+)_.*","\\1",OMNames_base)
commonNames <- bam_common_name_sub
lty <- c(1,2)

for(i in commonNames){
if(plot_pdf){pdf(paste0("Figs/Hist_",i,".pdf"))}  
rdat_name_i <- paste0("rdat_",i)

OM_i <- get(paste0("OM_",i))
# Data_i <- get(paste0("Data_",i))
Hist_i <- get(paste0("Hist_",i))
rdat_i <- standardize_rdat(get(rdat_name_i))
rdatmods_i <- rdatmods[[i]]

Nage_F0_pr_sc_i <- rdatmods_i$Nage_F0_pr_sc

Fmatrix <- Hist_i@TSdata$Find

# Landings
Lmatrix <- Hist_i@TSdata$Landings[,,1]+Hist_i@TSdata$Landings[,,2]
dimnames(Lmatrix) <- dimnames(Fmatrix)
Lbam <- t.series_i$total.L.klb
Dbam <- t.series_i$total.D.klb
if(!is.null(Dbam)){
  Lbam <- Lbam+Dbam
}
Lylim <- range(c(0,as.numeric(Lmatrix),Lbam))
plot_boot_vec(Lmatrix,CIpct=CIpct,xlab="year",ylab="Landings + Discards (1000 lb)",ylim=Lylim,lty=lty[1])
points(years_i,Lbam,type="o",#axes=FALSE,xlab="",ylab="",
     col="blue",lty=lty[2])

legend("bottomleft",
       legend=c("sim","BAM"),
       lty=lty,
       pch=c(NA,1),
       col=c("black","blue"),
       bg=rgb(1,1,1,0.5),
       inset=0.05
       )

# Indices
AddIndArray <- Hist_i@Data@AddInd
dimnames(AddIndArray) <- dimnames(OM_i@cpars$Data@AddInd)
nAddInd <- dim(AddIndArray)[2]
AddInd_col_sim <- grays(nAddInd)
AddInd_col_bam <- blues(nAddInd)

#U.names.ob <- names(t.series_i)[grepl("^U..*.ob$",names(t.series_i))]
bam.U.ob <- t.series_i[,paste0("U.",dimnames(AddIndArray)[[2]],".ob"),drop=FALSE]
for(j in 1:nAddInd){
AddIndmatrix_j <- AddIndArray[,j,]
dimnames(AddIndmatrix_j) <- dimnames(Fmatrix)  
plot_boot_vec(AddIndmatrix_j,add=ifelse(j!=1,TRUE,FALSE),
              CIpct=CIpct,xlab="year",ylab="AddInd",
              col_lines=AddInd_col_sim[j],lty=lty[1]
              )
points(as.numeric(rownames(bam.U.ob)),bam.U.ob[,j],type="o", col=AddInd_col_bam[j],lty=lty[2])

}
# Recruitment
Rmatrix <- Hist_i@AtAge$Number[,1,,1]+Hist_i@AtAge$Number[,1,,2]
dimnames(Rmatrix) <- dimnames(Fmatrix)
plot_boot_vec(Rmatrix,CIpct=CIpct,xlab="year",ylab="recruits",lty=lty[1])
points(years_i,t.series_i$recruits*Nage_F0_pr_sc_i,type="o", col="blue",lty=lty[2])

# N
Nmatrix <- Hist_i@TSdata$Number[,,1]+Hist_i@TSdata$Number[,,2]
dimnames(Nmatrix) <- dimnames(Fmatrix)
bam.N <- rowSums(rdatmods_i$N.age)
plot_boot_vec(Nmatrix,CIpct=CIpct,xlab="year",ylab="N",lty=lty[1])
points(years_i,bam.N,type="o",col="blue",lty=lty[2])

# F
# Fmatrix <- Hist_i@TSdata$Find
plot_boot_vec(Fmatrix,CIpct=CIpct,xlab="year",ylab="F",lty=lty[1])
 points(years_i,t.series_i$F.full,type="o",
     col="blue",lty=lty[2])

# B
Bmatrix <- Hist_i@TSdata$Biomass[,,1]+Hist_i@TSdata$Biomass[,,2]
dimnames(Bmatrix) <- dimnames(Fmatrix)
bam.Bklb <- rowSums(rdatmods_i$B.age)
plot_boot_vec(Bmatrix,CIpct=CIpct,xlab="year",ylab="Biomass (1000 lb)",lty=lty[1])
# par(new=TRUE)
points(years_i,bam.Bklb,type="o", #axes=FALSE,xlab="",ylab="",
     col="blue",lty=lty[1])

if(plot_pdf){dev.off()}
}
}
```
